### 2008-09-23 trunk/Latex/H2Preview/H2Prev2norm.tex

The results of the previous section can be adapted for the case where $W_r=I$.

We note again that:
% 
\begin{equation}
\nrm{T_{\tiny{\ma{r\\w}}\rightarrow z}}^2_2 =
\nrm{T_{w\rightarrow z}}^2_2+
\nrm{T_{r\rightarrow z}}^2_2. \label{proj_prop}
\end{equation}
%
As observed in Corollary~\ref{cor:minwandr}, the optimal preview controller minimises $\nrm{T_{w\rightarrow z}}_2$. Since $X_{gg}$ and $Y_g$ are the solutions to the DAREs associated with the problem of minimising $\nrm{T_{w\rightarrow z}}_2$, we may use the results in Sections \ref{subsec:stdH2FI} and \ref{subsec:stdH2OF} to write:
\als{
\gamma_{wc}^2&=\textrm{Tr}\left\{(D_{11gw}+D_{12}F_{0w})'(D_{11gw}+D_{12}F_{0w})\right.\\ &\left.\qquad+(B_{1gw}+B_{2g}F_{0w})'X_{gg}(B_{1gw}+B_{2g}F_{0w})\right\}\\
\gamma_{wf}^2&=\textrm{Tr}\left\{\bar R\left( (L_{0y}D_{21gw}-F_{0w})(L_{0y}D_{21gw}-F_{0w})'\right.\right.\\ &\left.\left.\qquad+(L_{0y}C_{2g}-F_{2g})Y_{gg}(L_{0y}C_{2g}-F_{2g})'\right) \right\}\\
\nrm{T_{w\rightarrow z}}^2_2&=\gamma_{wc}^2+\gamma_{wf}^2,
} 
which are independent of the preview length.

@@

\als{
X_{pp}=\sum^{N-1}_{j=0}{A_p^j}'(\hat Q - F_{2p}'\bar{R}F_{2p})A_p^j.
}
%
Note that post-multiplying by $A_p^kB_p$ has the effect of selecting individual block columns of the preceding matrix, that $C_pA_p^kB_p=0 \,\, \forall k \neq N-1$, and that $A_p^N=0$. This means that:
%
\[
B_p'X_{pp}B_p=B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0} - \sum_{j=0}^{N-2}S' A^j_{cg} B_{2g} {\bar R}^{-1} B_{2g}' {A^j_{cg}}' S,
\]
where $F_{2p0}$ is the left-most block column of $F_{2p}$ and is given by:
\begin{equation}
F_{2p0}=-\bar R^{-1}\left(B_{2g}'X_{gg}B_{1gr}+D_{12}'D_{11gr}\right). \label{eqn:F2p0}
\end{equation}
%
Combining this with (\ref{eqn:gamrmedeff}), and using (\ref{eqn:Xgp}), leads to 
\als{
\nrm{T_{r\rightarrow z}}^2_2=\tra{\underbrace{B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0}}_{\mbox{No preview}}-\underbrace{\sum_{j=0}^{N-1}S' A^j_{cg} B_{2g}{\bar R}^{-1} B_{2g}'{A^j_{cg}}'S}_{\mbox{Preview reduction}}}.
}
In order to judge how much preview to use, we need to know the value of the maximum possible improvement due to preview action. Suppose the matrix $\Gamma$ satisfies:
\als{
\Gamma=A_{cg}\Gamma A_{cg}'+B_{2g}\bar R^{-1}B_{2g}'
,}
which implies that:
\als{
\Gamma=\sum_{j=0}^{\infty}A_{cg}^jB_{2g}\bar R ^{-1}B_{2g}'{A_{cg}'}^{j}
.}
Thus the reduction in $\nrm{T_{r\rightarrow z}}_2^2$ due to preview is bounded above by 
\[
\tra{S'\Gamma S},
\]
and evaluating this limit only requires the solution of an $n_g$-dimensional Lyapunov equation.
This provides a useful bound on the achievable norm reduction one might obtain using preview. For example, one could continue adding preview points, until 95\%  of the maximum possible benefit had been achieved.

>>>>

It is easy to check that the results of the previous sections carry over for $W_r=I$. All that is required is to remove the  gains associated with the states of $W_r$.

We note again that:
% 
\begin{equation}
\nrm{T_{{[r'\,\,w']'}\rightarrow z}}^2_2 =
\nrm{T_{w\rightarrow z}}^2_2+
\nrm{T_{r\rightarrow z}}^2_2. \label{proj_prop}
\end{equation}
%
As observed in Corollary~\ref{cor:minwandr}, the optimal preview controller minimises $\nrm{T_{w\rightarrow z}}_2$. Since $X_{gg}$ and $Y_g$ are the solutions to the DAREs associated with the problem of minimising $\nrm{T_{w\rightarrow z}}_2$, we may use the results in Sections \ref{subsec:stdH2FI} and \ref{subsec:stdH2OF} to write:
\als{
\gamma_{wc}^2&=\textrm{Tr}\left\{(D_{11gw}+D_{12}F_{0w})'(D_{11gw}+D_{12}F_{0w})\right.\\ &\left.\qquad+(B_{1gw}+B_{2g}F_{0w})'X_{gg}(B_{1gw}+B_{2g}F_{0w})\right\}\\
\gamma_{wf}^2&=\textrm{Tr}\left\{\bar R\left( (L_{0y}D_{21gw}-F_{0w})(L_{0y}D_{21gw}-F_{0w})'\right.\right.\\ &\left.\left.\qquad+(L_{0y}C_{2g}-F_{2g})Y_{gg}(L_{0y}C_{2g}-F_{2g})'\right) \right\}\\
\nrm{T_{w\rightarrow z}}^2_2&=\gamma_{wc}^2+\gamma_{wf}^2,
} 
which are independent of the preview length.

@@

\als{
X_{pp}=\sum^{N-1}_{j=0}{A_p^j}'(\hat Q - F_{2p}'\bar{R}F_{2p})A_p^j.
}
%
Note that post-multiplying by $A_p^kB_p$ has the effect of selecting individual block columns of the preceding matrix, that $C_pA_p^kB_p=0 \,\, \forall k \neq N-1$, and that $A_p^N=0$. This means that:
%
\[
B_p'X_{pp}B_p=B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0} - \sum_{j=0}^{N-2}S' A^j_{cg} B_{2g} {\bar R}^{-1} B_{2g}' {A^j_{cg}}' S,
\]
where $F_{2p0}$ is the left-most block column of $F_{2p}$ and is given by:
\begin{equation}
F_{2p0}=-\bar R^{-1}\left(B_{2g}'X_{gg}B_{1gr}+D_{12}'D_{11gr}\right). \label{eqn:F2p0}
\end{equation}
%
Combining this with (\ref{eqn:gamrmedeff}), and using (\ref{eqn:Xgp}), leads to 
\aln{
\nrm{T_{r\rightarrow z}}^2_2=\tra{\underbrace{B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0}}_{\mbox{Zero preview}}-\underbrace{\sum_{j=0}^{N-1}S' A^j_{cg} B_{2g}{\bar R}^{-1} B_{2g}'{A^j_{cg}}'S}_{\mbox{Preview reduction}}}.
\label{eqn:H2CostSplit}}
In order to judge how much preview to use, we need to know the value of the maximum possible improvement due to preview action. Suppose the matrix $\Gamma$ satisfies:
\als{
\Gamma=A_{cg}\Gamma A_{cg}'+B_{2g}\bar R^{-1}B_{2g}'
,}
which implies that:
\als{
\Gamma=\sum_{j=0}^{\infty}A_{cg}^jB_{2g}\bar R ^{-1}B_{2g}'{A_{cg}'}^{j}
.}
Comparing this to (\ref{eqn:H2CostSplit}), it follows that the reduction in $\nrm{T_{r\rightarrow z}}_2^2$ due to preview is bounded above by 
\[
\tra{S'\Gamma S},
\]
and evaluating this limit only requires the solution of an $n_g$-dimensional Lyapunov equation (in addition to the $n_g$ dimensional DARE required to evaluate $S$). The following quantity provides a useful measure of the fraction of the maximum norm reduction that has been achieved:
\aln{\gamma_{\,_{\%,imp}}=100\times \tra{S'\Gamma S}^{-1}{\left(\sum_{j=0}^{N-1}S' A^j_{cg} B_{2g}{\bar R}^{-1} B_{2g}'{A^j_{cg}}'S\right)}.\label{eqn:gamimp}} 
%This provides a useful bound on the achievable norm reduction one might obtain using preview. 
This can be used to determine how much preview to use; for example, one might continue adding preview points until $\gamma_{\,_{\%,imp}} >99\%$.
